---
title: "AssayDevelopment"
author: "Zachary Noel"
date: "5/3/2017"
output:
  md_document:
    variant: markdown_github
---

```{r eval=FALSE, include=FALSE}
rm(list = ls(all=TRUE)) # removes all variables in the global environment so you start fresh

Sys.time() # prints out the time and date you ran the code

options(scipen = 999) # stops anything from being in scientific notation
```

```{r setup, echo = FALSE, include=FALSE}
# ipak function: install and load multiple R packages.
# check to see if packages are installed. Install them if they are not, then load them into the R session.
# Source: https://gist.github.com/stevenworthington/3178163
ipak <- function(pkg){
new.pkg <- pkg[!(pkg %in% installed.packages()[,"Package"])]
if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
sapply(pkg, require, character.only = TRUE)
}
```

###Libraries
```{r libraries, echo=FALSE, message=FALSE}
packages <- c("drc","ggplot2", "lsmeans", "lmerTest", "plotrix", "plyr", "knitr")
ipak(packages)
```

```{r read data}
agar.dil <- data.frame(read.csv("agardilutions.csv", na.strings = "na"))
```

###Assay Development

Here we are analysing a dataset where we inoculated different volumes of macerated agar in the wells of a 96 well plate to see how the fungicide and assay would perform under these conditions.

Here we are testing if the difference in macerated agar volume increased the background noise. 
We will pull out only the blank wells and do an ANOVA, treating trial as a random factor to test the affect of agar volume on optical density
```{r ANOVA0}
agar.dil.blank <- agar.dil[agar.dil$is == "BLANK",]

lm <- lmer(od600 ~ agarvol + (1|trial), data = agar.dil.blank)
anova(lm)
```

###Linear model of percent relative growth
```{r DATA CLEAN}
#doing a little data clean up, taking out the blank and ntc wells
noblank <- c("BLANK","NTC")
agar.dilnoblank <- agar.dil[!agar.dil$is %in% noblank,]
agar.dilnoblank$agarvol <- as.factor(agar.dilnoblank$agarvol) #convert the numeric data to factor
agar.dilnoblank$relgrow[agar.dilnoblank$conc == 10] <- agar.dilnoblank$relgrow[agar.dilnoblank$conc == 10]*100

agar.dilnoblank$relgrow[agar.dilnoblank$conc == 0.5] <- agar.dilnoblank$relgrow[agar.dilnoblank$conc == 0.5]*100
```

Testing if the percent realative growth at 0.5 ppm was increased by the agar volume
We do have one missing value that was a contaminated well
```{r ANOVA1}
rg_aov.05 <- lmer(relgrow ~ agarvol + (1|is), data = agar.dilnoblank[agar.dilnoblank$conc == 0.5,])
summary(rg_aov.05)
lmerTest::anova(rg_aov.05, type = 1) # type 1 SS ANOVA table, balanced design all types are the same 
```

Lets make sure we look at the regression diagnostics
```{r Regression Diag1.}
plot(rg_aov.05)
qqnorm(resid(rg_aov.05)); qqline(resid(rg_aov.05))
hist(resid(rg_aov.05))
```

Get the LS MEANS
```{r LSMEANS1}
# lsmeans for our linear model
lm_lsmeans_rg <- lsmeans::lsmeans(rg_aov.05, c("agarvol"))
plot(lm_lsmeans_rg)
lm_lsmeans_rg
Results_rg_aov05 <- cld(lm_lsmeans_rg, alpha = 0.05, adjust = "tuk", Letters = letters, reversed = FALSE)
```

Testing if the percent realative growth at 10 ppm was increased by the agar volume
We do have one missing value that was a contaminated well
```{r ANOVA2}
rg_aov.10 <- lmer(relgrow ~ agarvol + (1|is), data = agar.dilnoblank[agar.dilnoblank$conc == 10,])
summary(rg_aov.10)
lmerTest::anova(rg_aov.10, type = 1) # type 1 SS ANOVA table, balanced design all types are the same 
```

Lets make sure we look at the regression diagnostics
```{r Regression Diag.}
plot(rg_aov.10)
qqnorm(resid(rg_aov.10)); qqline(resid(rg_aov.10))
hist(resid(rg_aov.10))
```

Get the LS MEANS
```{r LSMEANS}
# lsmeans for our linear model
lm_lsmeans_rg <- lsmeans::lsmeans(rg_aov.10, c("agarvol"))
plot(lm_lsmeans_rg)
lm_lsmeans_rg
Results_rg_aov10 <- cld(lm_lsmeans_rg, alpha = 0.05, adjust = "tuk", Letters = letters, reversed = FALSE)
```

###EC50 estimation

The following loop will generate EC50's for each isolate, agar volume, trial combination and save that output into a data frame called agardil, to use later for an ANOVA
```{r EC50 loop, warning=FALSE, echo=TRUE, results="hide", message=FALSE}
agar.dil <- agar.dil[!agar.dil$is == "BLANK",]
agar.dil <- agar.dil[!agar.dil$is == "NTC",]
agar.dil$is <- factor(agar.dil$is)
agardil <- NULL
nm <- levels(agar.dil$is)
for (t in 1:2){
    for (i in seq_along(nm)){
agardil.drc <- drm(100*relgrow ~ conc, 
                   curveid = agarvol, 
                   data = agar.dil[agar.dil$is == nm[[i]] & agar.dil$trial == t,], 
                   fct = LL.4())

summary.mef.fit <- data.frame(summary(agardil.drc)[[3]])
#outputs the summary of just the EC50 data including the estimate, standard error, upper and lower bounds of the 95% confidence intervals around the EC50
print(nm[[i]])
print("RELATIVE EC50")
EC50.od.rel <- data.frame(ED(agardil.drc, 
                             respLev = c(50), 
                             type = "relative",
                             interval = "delta"),
                          level = 0.95)
rel.ec50 <- EC50.od.rel[1][[1]]
print("ABSOLUTE EC50")
EC50.od.abs <- data.frame(ED(agardil.drc, 
                             respLev = c(50), 
                             type = "absolute",
                             interval = "delta"),
                          level = 0.95)
abs.ec50 <- EC50.od.rel[1][[1]]
print(summary.mef.fit)
print("LACK FIT")
fit <- modelFit(agardil.drc)
lackfitpvalue <- fit[5]$`p value`[2]
print(fit)
print("COMP EC50")
#SI(agardil.drc, c(50, 50), ci = "delta")
agar.vol <- unique(agar.dil$agarvol[agar.dil$is == nm[[i]]])
agardil_i <- data.frame(rep(nm[[i]], 4), c(agar.vol), rep(t, 4), c(abs.ec50))
agardil <- rbind.data.frame(agardil, agardil_i)
   }

}
colnames(agardil) <- c("is", "agar.vol", "trial", "EC50")
```

##Linear models to describe these data: 

model: EC50 as a function of agar volume and isolate as a random effect 

We are treating isolate as a random effect because these four isolates were chosen at random from a larger population of isolates and we want to generalize over isolate to see the effect of agar volume on the EC50. 

```{r ANOVA3}
agardil$agar.vol <- as.factor(agardil$agar.vol) #convert the numeric data to factor
agardil_aov <- lmer(EC50 ~ agar.vol + (1|is), data = agardil)
summary(agardil_aov)
lmerTest::anova(agardil_aov, type = 1) # type 1 SS ANOVA table, balanced design all types are the same 
```

Lets make sure we look at the regression diagnostics
```{r Regression Diag2.}
plot(agardil_aov)
qqnorm(resid(agardil_aov)); qqline(resid(agardil_aov))
```

The residuals look normally destributed. One could argue the need for a log transformation for a "V" shaped residual plot, but I've already tried that and the contrasts do not change so I am keeping these data non-transformed. 

```{r LSMEANS2}
# lsmeans for our linear model
lm_lsmeans <- lsmeans::lsmeans(agardil_aov, c("agar.vol"))
plot(lm_lsmeans)
lm_lsmeans
Results_EC50_aov <- cld(lm_lsmeans, alpha = 0.05, adjust = "tuk", Letters = letters, reversed = FALSE)
```

Just getting the acctual SE for the cell means of agar volume. 
```{r CELLMEANS}
mean.agar <- ddply(agardil, c("agar.vol"), 
      summarise, 
      mean = mean(EC50, na.rm = TRUE),
      std.err = std.error(EC50, na.rm = TRUE))
mean.agar$contrasts <- Results_EC50_aov$.group
mean_rg10 <- ddply(agar.dilnoblank[agar.dilnoblank$conc == 10,], c("agarvol"),
                 summarise, 
                 mean = mean(relgrow, na.rm = TRUE), 
                 std.err = std.error(relgrow, na.rm = TRUE))
mean_rg10$contrasts <- Results_rg_aov10$.group
mean_rg05 <- ddply(agar.dilnoblank[agar.dilnoblank$conc == 0.5,], c("agarvol"),
                 summarise, 
                 mean = mean(relgrow, na.rm = TRUE), 
                 std.err = std.error(relgrow, na.rm = TRUE))
mean_rg05$contrasts <- Results_rg_aov05$.group
FINAL.TABLE <- cbind.data.frame(mean.agar, mean_rg10$mean, mean_rg10$std.err, mean_rg10$contrasts, mean_rg05$mean, mean_rg05$std.err, mean_rg05$contrasts)
colnames(FINAL.TABLE) <- c("Agar Volume", "Mean EC50", "EC50.SE", "EC50.Contrast", "Mean RG 10", "RG10.SE", "RG10.Contrast", "Mean RG 05", "RG05.SE", "RG05.Contrast")
```

```{r FINAL TABLE}
kable(FINAL.TABLE, digits = 3)
```
