---
title: "Method_Correlation"
author: "Zachary Noel"
date: "May 2, 2016"
output: 
  md_document:
    variant: markdown_github
---

```{r Setting options, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls(all=TRUE)) # removes all variables in the global environment so you start fresh

Sys.time() # prints out the time and date you ran the code

options(scipen = 999) # stops anything from being in scientific notation
```

A function to do a t-test to determine if varias values in a linear model is significantly different than others. 
Arguments:
reg = the linear model 
coefnum = 1 = intercept, 2 = beta ...
val = value you would like to test, the default lm tests if value is significantly different from zero. 
```{r Functions, include=FALSE}
ttest <- function(reg, coefnum, val){
  co <- coef(summary(reg))
  tstat <- (co[coefnum,1]-val)/co[coefnum,2]
  2 * pt(abs(tstat), reg$df.residual, lower.tail = FALSE)
} 

# ipak function: install and load multiple R packages.
# check to see if packages are installed. Install them if they are not, then load them into the R session.
# Source: https://gist.github.com/stevenworthington/3178163
ipak <- function(pkg){
new.pkg <- pkg[!(pkg %in% installed.packages()[,"Package"])]
if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
sapply(pkg, require, character.only = TRUE)
}
```

###Libraries
```{r}
packages <- c("drc", "lme4", "lsmeans", "plyr", "plotrix", "knitr", "ggplot2", "lmtest", "lmerTest", "Rmisc", "gridExtra", "plotly", "webshot", "ggpmisc", "ggsci","scales")
ipak(packages)
```


###Read Data
```{r Reading in data, message=FALSE, warning=FALSE, include=FALSE}
cor <- data.frame(read.csv("correlation.csv", na.strings = "na"))
cor <- data.frame(na.omit(cor)) #omits missing values
```

This function will run a linear model of the percent relative growth, as well as correlations in both pearson and spearman and will also plot it in ggplot, if desired.

data = data.frame
concentration = concentration
plot = logical

```{r Function for relative growth}
RelGrowth.lm <- function(data, concentration, plot){
  data.string.y <- data$odrelgrowth[data$conc == concentration]
  data.string.x <- data$ppmeanrelgrowth[data$conc == concentration]
  lin.mod <- lm(data.string.y ~ data.string.x)
  sum.linmod <- summary(lin.mod)
  pearson <- cor.test(data.string.x, data.string.y, method = "pearson")
  spearman <- cor.test(data.string.x, data.string.y, method = "spearman")
  beta <- ttest(lin.mod, 2, 1) # t-test for Beta significantly different than one
  bias <- (sum.linmod[[4]][2] - 1)*100 #percent Bias
  coeff.var <- (sum.linmod[[4]][4]/sum.linmod[[4]][2])*100
  if(plot == TRUE){
  p <- ggplot(data[data$conc == concentration,], aes(y = odrelgrowth, x = ppmeanrelgrowth)) +
    geom_point(aes(colour = factor(species))) +
    guides(colour = guide_legend(title = "Species")) +
    scale_y_continuous(limits = c(0, 110), breaks = c(0, 25, 50, 75, 100)) +
    scale_x_continuous(limits = c(0, 110), breaks = c(0, 25, 50, 75, 100)) +
    geom_smooth(method = "lm", se = FALSE, fullrange = TRUE, col = "black") +
    xlab("% Poison Plate Growth, relative to control") + 
    ylab("% Optical Density growth, relative to control") + 
    theme_bw() +
    theme(axis.text.x = element_text(size = 10, face = "bold"),
          axis.text.y = element_text(size = 10, face = "bold"),
          axis.title.x = element_text(size = 15, face = "bold"),
          axis.title.y = element_text(size = 15, face = "bold"),
          legend.text = element_text(size = 10, face = "bold.italic"),
          legend.key = element_blank(),
          legend.title = element_text(size = 15, face="bold"))
  results <- list(sum.linmod, pearson, spearman, beta, bias, coeff.var, p)
  names(results) <- c("lm", "pearson", "spearman", "beta.t", "per.bias","coeff.var", "plot")
  return(results)
  } else {
    results <- list(sum.linmod, pearson, spearman, beta, bias, coeff.var)
    names(results) <- c("lm", "pearson", "spearman", "beta.t", "per.bias", "coeff.var")
    return(results)
  }
}
```

We want to look at the correlation of the two methods, poison plate and optical density, to determine if the optical density method is any good.

Ethaboxam relative growth correlations
```{r Ethaboxam Relative Growth}
eth.cor.pp <- ddply(cor[cor$chem == "ethaboxam" & cor$method == "poison_plate",], c("is", "species", "conc"), 
      summarize, 
      ppmeanrelgrowth = 100*mean(relgrowth, na.rm = TRUE))
eth.cor.od <- ddply(cor[cor$chem == "ethaboxam" & cor$method == "optical_density",], c("is", "species", "conc"), 
      summarize, 
      odmeanrelgrowth = 100*mean(relgrowth, na.rm = TRUE))
eth.cor <- cbind.data.frame(eth.cor.pp, eth.cor.od$odmeanrelgrowth)

colnames(eth.cor) <- c("is", "species", "conc", "ppmeanrelgrowth", "odrelgrowth")
eth.001 <- RelGrowth.lm(eth.cor, concentration = 0.01, plot = TRUE)
eth.001
eth.01 <- RelGrowth.lm(eth.cor, concentration = 0.1, plot = TRUE)
eth.01
eth.05 <- RelGrowth.lm(eth.cor, concentration = 0.5, plot = TRUE)
eth.05
eth.1 <- RelGrowth.lm(eth.cor, concentration = 1, plot = TRUE)
eth.1
eth.5 <- RelGrowth.lm(eth.cor, concentration = 5, plot = TRUE)
eth.5
eth.20 <- RelGrowth.lm(eth.cor, concentration = 20, plot = TRUE)
eth.20
```

Mefenoxam relative growth correlations
```{r Mefenoxam relative growth}
mef.cor.pp <- ddply(cor[cor$chem == "mefenoxam" & cor$method == "poison_plate",], c("is", "species", "conc"), 
      summarize, 
      ppmeanrelgrowth = 100*mean(relgrowth, na.rm = TRUE))
mef.cor.od <- ddply(cor[cor$chem == "mefenoxam" & cor$method == "optical_density",], c("is", "species", "conc"), 
      summarize, 
      odmeanrelgrowth = 100*mean(relgrowth, na.rm = TRUE))
mef.cor.od <- mef.cor.od[!mef.cor.od$conc == 100,]
mef.cor.pp <- mef.cor.pp[!mef.cor.pp$conc == 100,]
mef.cor <- cbind.data.frame(mef.cor.pp, mef.cor.od$odmeanrelgrowth)
colnames(mef.cor) <- c("is", "species", "conc", "ppmeanrelgrowth", "odrelgrowth")
mef.001 <- RelGrowth.lm(mef.cor, concentration = 0.01, plot = TRUE)
mef.001
mef.01 <- RelGrowth.lm(mef.cor, concentration = 0.1, plot = TRUE)
mef.01
mef.05 <- RelGrowth.lm(mef.cor, concentration = 0.5, plot = TRUE)
mef.05
mef.1 <- RelGrowth.lm(mef.cor, concentration = 1, plot = TRUE)
mef.1
mef.10 <- RelGrowth.lm(mef.cor, concentration = 10, plot = TRUE)
mef.10
```

From the analysis above it looks like there are some isolates with percent relative growth above 50% at the highest concentration tested. Therefore those isolates will not have an EC50 and cannot be calculated. We will express these isolates in terms of their relative growth. 
```{r Insensitive isolates}
# briefly we are going to split up the data frame into each concentration to make it easier to take out individual isolates
cor_eth <- cor[cor$chem == "ethaboxam",]
cor_mef <- cor[cor$chem == "mefenoxam",]

# taking out insensitive isolates, otherwise convergence would not occur with the ll.4 model
insens_iso_eth <- c("MISO_8-29.1", "C-MNSO2_2-21", "NDSO_L-8-6", "ILSO_6-15C")
insens_iso_mef <- c("V-MISO2_6-46", "23.4B", "1.18A")

# creating a dataframe with only those isolates
insenscor_eth <- cor_eth[cor_eth$is %in% insens_iso_eth,]
insenscor_mef <- cor_mef[cor_mef$is %in% insens_iso_mef,]

# taking out those isolates
cor_eth <- cor_eth[!cor_eth$is %in% insens_iso_eth,]
cor_mef <- cor_mef[!cor_mef$is %in% insens_iso_mef,]
cor_eth$is <- factor(cor_eth$is)
cor_mef$is <- factor(cor_mef$is)

cor <- rbind.data.frame(cor_eth, cor_mef)
```

This code iterates through every isolate and generates a relative and absolute EC50 using the LL.4 model of drc and saves the output. I already went through and picked out the isolates for both mefenoxam and ethaboxam that have an EC50 beyond the concentration range tested in this study. 
```{r EC50, warning=FALSE, results="hide", message=FALSE}

relative <- function(data){
  EC50.pp.rel <- data.frame(ED(data, 
                             respLev = c(50), 
                             type = "relative",
                             interval = "delta"),
                          level = 0.95)
rel.ec50.pp <- EC50.pp.rel[1][[1]]
return(rel.ec50.pp)
}
absolute <- function(data){
  EC50.pp.abs <- data.frame(ED(data, 
                             respLev = c(50), 
                             type = "absolute",
                             interval = "delta"),
                          level = 0.95)
abs.ec50.pp <- EC50.pp.abs[1][[1]]
return(abs.ec50.pp)
}
plug_EC <- function(chemistry){
  nm <- unique(cor$is[cor$chem == as.character(chemistry)])
dataframe_names <- c("is", "species", "method", "trial", "chem", "absolute", "relative")
meth.cor <- NULL
for (i in seq_along(nm)){
mefcor.pp.drc <- drm(100*relgrowth ~ conc, data = cor[cor$is == nm[[i]] & cor$method == "poison_plate" & cor$chem == as.character(chemistry),], curveid = trial, fct = LL.4(), na.action = na.omit)
mefcor.od.drc <- drm(100*relgrowth ~ conc, data = cor[cor$is == nm[[i]] & cor$method == "optical_density" & cor$chem == as.character(chemistry),], curveid = trial, fct = LL.4(), na.action = na.omit)
paste(print(nm[[i]]))
# RELATIVE 
rel.pp.mef <- relative(mefcor.pp.drc)
rel.od.mef <- relative(mefcor.od.drc)

# ABSOLUTE 
abs.pp.mef <- absolute(mefcor.pp.drc)
abs.od.mef <- absolute(mefcor.od.drc)

mef.cor_od <- data.frame(cbind.data.frame( 
                  nm[[i]], 
                  as.character(unique(cor$species[cor$is == nm[[i]]])),
                  as.character(unique(cor$method[cor$is == nm[[i]] & cor$method == "optical_density"])),
                  unique(cor$trial[cor$is == nm[[i]] & cor$method == "optical_density"]),
                  as.character(chemistry),
                  as.numeric(abs.od.mef),
                  as.numeric(rel.od.mef)))
colnames(mef.cor_od) <- dataframe_names
mef.cor_pp <- data.frame(cbind.data.frame( 
                  nm[[i]], 
                  as.character(unique(cor$species[cor$is == nm[[i]]])),
                  as.character(unique(cor$method[cor$is == nm[[i]] & cor$method == "poison_plate"])),
                  unique(cor$trial[cor$is == nm[[i]] & cor$method == "poison_plate"]),
                  as.character(chemistry),
                  as.numeric(abs.pp.mef),
                  as.numeric(rel.pp.mef)))
colnames(mef.cor_pp) <- dataframe_names

meth.cor <- rbind.data.frame(meth.cor, mef.cor_od, mef.cor_pp)
  }
return(meth.cor)
}

mefenoxam_ec50 <- plug_EC("mefenoxam")
ethaboxam_ec50 <- plug_EC("ethaboxam")

ec50_cor <- rbind.data.frame(ethaboxam_ec50, mefenoxam_ec50)
dim(ec50_cor)

# not sure why one of the isolates had duplicates but they did, so this code will find duplicates in the absolute ec50s and delete the entire row. 
ec50_cor <- ec50_cor[-which(duplicated(ec50_cor$absolute)),] 
dim(ec50_cor)
```

Table of EC50 values for every isolate tested for both mefenoxam and ethaboxam on both poison plate and optical density method. 
```{r EC50 Table, warning=FALSE, echo=FALSE, message=FALSE}
EC50.cor <- ddply(ec50_cor, c("is", "species", "chem", "method"), 
      summarise, 
      mean.abs = mean(absolute, na.rm = TRUE),
      std.abs = std.error(absolute, na.rm = TRUE),
      mean.rel = mean(relative, na.rm = TRUE),
      std.rel = std.error(relative, na.rm = TRUE))
kable(EC50.cor)
```

Lets do an ANOVA for each chemistry and the effect of method. 

model 1: method as fixed effect and isolate as random effect 

We are treating isolate as a random effect because we we sampled these isolates from a larger possible population of isolates and we want to generalize over all isolates
```{r}
lm_mef <- lmer(absolute ~ method + (1|is), data = ec50_cor[ec50_cor$chem == "mefenoxam",])
hist(residuals(lm_mef)) # not normally distributed residuals 
qqnorm(resid(lm_mef), main = "not log transformed"); qqline(resid(lm_mef))
lm_mef <- lmer(log(absolute) ~ method + (1|is), data = ec50_cor[ec50_cor$chem == "mefenoxam",])
hist(residuals(lm_mef)) # log transformation is good
qqnorm(resid(lm_mef), main = "log transformed"); qqline(resid(lm_mef))

lmerTest::anova(lm_mef, test.statistic="F", type = 2) # using type II ANOVA for unbalanced data. Some isolates have more technical replicates than others. So the mean over all isolates is different.  
plot(lm_mef, type = c("p", "smooth"), id = 0.05) # regression diagnostics
lsmeans_mef <- lsmeans::lsmeans(lm_mef, "method")
plot(lsmeans_mef)
```
This is what we expected, no significant differnces for the method.

Lets do the same for ethaboxam.
```{r}
lm_eth <- lmer(absolute ~ method + (1|is), data = ec50_cor[ec50_cor$chem == "ethaboxam",])
hist(residuals(lm_eth)) # not normally distributed residuals 
qqnorm(resid(lm_eth), main = "not log transformed"); qqline(resid(lm_eth))

lm_eth <- lmer(log(absolute) ~ method + (1|is), data = ec50_cor[ec50_cor$chem == "ethaboxam",])
hist(residuals(lm_eth)) # not normally distributed residuals 
qqnorm(resid(lm_eth), main = "log transformed"); qqline(resid(lm_eth))

lmerTest::anova(lm_eth, test.statistic="F", type = 2) # using type II ANOVA for unbalanced data. Some isolates have more technical replicates than others. So the mean over all isolates is different.  
plot(lm_eth, type = c("p", "smooth"), id = 0.05)# regression diagnostics
lsmeans_eth <- lsmeans::lsmeans(lm_eth, "method")
plot(lsmeans_eth)
```

Now lets put chemistry in as a fixed effect and fit the interaction bewtween chemistry and method. 

We have log-transformed these data for homogienity of variance 
```{r}
lm3 <- lm(log(absolute) ~ is * chem * method, data = ec50_cor)
hist(residuals(lm3)) # log transformation is good
qqnorm(resid(lm3), main = "log transformed"); qqline(resid(lm3))
anova(lm3)
```

```{r}
#Plotting diagnostic plots for fit1 model
par(mfrow=c(2,2)) # optional layout 
plot(lm3)# diagnostic plotspar
(mfrow=c(1,1)) # optional layout

lsmeans3 <- lsmeans::lsmeans(lm3, c("is", "chem", "method"))
plot(lsmeans3)
```


Lets do correlation analysis between the two methods separated by chemistry.
```{r, include = FALSE}
# we are just adjusting the dataset here to get it in a good plotting format
EC50_pp <- EC50.cor[EC50.cor$method == "poison_plate",]
colnames(EC50_pp) <- c("is", "species_pp", "chem", "method", "mean.abs.pp", "std.abs.pp", "mean.rel.pp", "std.rel.pp")
EC50_od <- EC50.cor[EC50.cor$method == "optical_density",]
colnames(EC50_od) <- c("is", "species_od", "chem", "method", "mean.abs.od", "std.abs.od", "mean.rel.od", "std.rel.od")
EC50 <- cbind.data.frame(EC50_pp, EC50_od)
```

We are testing the correlation of the absolute EC50s between the two methods. 
We are going to use spearman's correlation coeffiecient since it is rank based it can handle outliers with high leverage. 
```{r}
cor_mef <- lm(mean.abs.pp ~ mean.abs.od, data = EC50[EC50$chem == "mefenoxam",])
summary(cor_mef)
par(mfrow = c(2,2))
plot(cor_mef)
(mfrow=c(1,1)) # optional layout
ttest(cor_mef, 1, 0) # tests if intercept is significantly different than 0
ttest(cor_mef, 2, 1) # tests if slope (beta) is significantly different than 1
(summary(cor_mef)[[4]][2] - 1)*100 #percent Bias
``` 
There is a significant linear relationship between the mean absolute EC50 using either method. Since it looked like there were some points with a bit of leverage we will use spearman's correlation to test the significance of the correlation.We will also look at the spearman:pearson correlation ratio to see if the correlation is more monotonic or linear. 

```{r}
spear.cor.mef <- cor.test(EC50$mean.abs.pp[EC50$chem == "mefenoxam"], 
         EC50$mean.abs.od[EC50$chem == "mefenoxam"], 
         method = "spearman")
pear.cor.mef <- cor.test(EC50$mean.abs.pp[EC50$chem == "mefenoxam"], 
         EC50$mean.abs.od[EC50$chem == "mefenoxam"], 
         method = "pearson")
spear.cor.mef
pear.cor.mef
```
Since the spearman correlation coeficient is lower than the pearson coefficient, this indicates we have more of a linear relationship than a monotonic one. This is a good thing because we would expect a perfect linear relationship between the methods. 

```{r}
cor_eth <- lm(mean.abs.pp ~ mean.abs.od, data = EC50[EC50$chem == "ethaboxam",])
summary(cor_eth)
```
```{r}
par(mfrow = c(2,2))
plot(cor_eth)
```
```{r}
ttest(cor_eth, 1, 0) # tests if intercept is significantly different than 0
ttest(cor_eth, 2, 1) # tests if slope (beta) is significantly different than 1
(summary(cor_eth)[[4]][2] - 1)*100 #percent Bias
``` 
There is a significant linear relationship between the mean absolute EC50 using either method. Since it looked like there were some points with a bit of leverage we will use spearman's correlation to test the significance of the correlation.

```{r}
spear.cor.eth <- cor.test(EC50$mean.abs.pp[EC50$chem == "ethaboxam"], 
         EC50$mean.abs.od[EC50$chem == "ethaboxam"], 
         method = "spearman")
pear.cor.eth <- cor.test(EC50$mean.abs.pp[EC50$chem == "ethaboxam"], 
         EC50$mean.abs.od[EC50$chem == "ethaboxam"], 
         method = "pearson")
spear.cor.eth
pear.cor.eth
```

```{r}
spear.cor.mef <- cor.test(EC50$mean.abs.pp[EC50$chem == "mefenoxam"], 
         EC50$mean.abs.od[EC50$chem == "mefenoxam"], 
         method = "spearman")
pear.cor.mef <- cor.test(EC50$mean.abs.pp[EC50$chem == "mefenoxam"], 
         EC50$mean.abs.od[EC50$chem == "mefenoxam"], 
         method = "pearson")
spear.cor.mef
pear.cor.mef
```

```{r, fig.height=3, fig.width=6}
EC50_spec <- ddply(EC50, c("species_od","chem", "method"), 
      summarize, 
      mean.abs.pp = mean(mean.abs.pp, na.rm = TRUE),
      std.abs.pp = std.error(std.abs.pp, na.rm = TRUE),
      mean.abs.od = mean(mean.abs.od, na.rm = TRUE),
      std.abs.od = std.error(std.abs.od, na.rm = TRUE))

ggplot(EC50_spec, aes(mean.abs.pp, mean.abs.od)) + 
  geom_point(aes(colour = species_od, shape = chem)) +
  #geom_errorbarh(aes(xmax = mean.abs.pp + std.abs.pp, xmin = mean.abs.pp - std.abs.pp, height = .01)) +
  #geom_errorbar(aes(ymax = mean.abs.od + std.abs.od, ymin = mean.abs.od - std.abs.od, width = .01)) +
  geom_smooth(method = "lm", se = FALSE) + 
  theme_bw() +
  guides(colour = guide_legend(title = "Species"),
         shape = guide_legend(title = "Chemistry")) + 
  xlab(expression(bold("Poison Plate EC"[50]))) + 
  ylab(expression(bold("Optical Density EC"[50]))) + 
  scale_y_continuous(limits = c(0, 2), breaks = c(0, 0.5, 1, 1.5, 2)) +
  scale_x_continuous(limits = c(0, 2), breaks = c(0, 0.5, 1, 1.5, 2)) +
  theme(axis.text.x = element_text(family = "Times New Roman", size = 10, face = "bold"),
          axis.text.y = element_text(family = "Times New Roman", size = 10, face = "bold"),
          axis.title.x = element_text(family = "Times New Roman", size = 10, face = "bold"),
          axis.title.y = element_text(family = "Times New Roman", size = 10, face = "bold"),
          legend.text = element_text(family = "Times New Roman", size = 10, face = "bold.italic"),
          legend.key = element_blank(),
          legend.title = element_text(family = "Times New Roman", size = 15, face="bold"),
   strip.text.x = element_text(family = "Times New Roman",size = 15, face = "bold"))
```

```{r}
summary(lm(mean.abs.pp ~ mean.abs.od, data = EC50_spec))
```

Based on the above analysis, we will select the relative growth at 0.5
```{r}
mef.cor$chem <- "Mefenoxam"
eth.cor$chem <- "Ethaboxam"
cor.plot.relgrowth <- rbind.data.frame(eth.cor[eth.cor$conc == 0.5,], mef.cor[mef.cor$conc == 0.5,])
EC50$chem2 <- factor(EC50$chem, labels = c("Ethaboxam", "Mefenoxam"))
length(levels(cor.plot.relgrowth$is))

label.names.p <- c("Phytophthora sansomeana", 
                 "Phytophthora sojae", 
                                 "Phytopythium litorale",
                                 "Phytopythium megacarpum", 
                                 "Pythium aff. dissotocum", 
                                 "Pythium aphanidermatum", 
                                 "Pythium glomeratum", 
                                 "Pythium intermedium",
                                 "Pythium irregulare",
                                 "Pythium lutarium",
                                 "Pythium oopapillum",
                                 "Pythium perplexum",
                                 "Pythium pleroticum",
                                 "Pythium spinosum",
                                 "Pythium sylvaticum",
                                 "Pythium torulosum",
                                 "Pythium ultimum", 
                                 "Pythium ultimum var. sporangiiferum",
                                 "Pythium ultimum var. ultimum")

shape.p <- c(4,4,18,18,19,8,15,17,17,19,19,10,7,17,17,19,15,15,15)
color.names.p <- rep(pal_npg("nrc")(10),3)
labels <- data.frame(label.names.p, shape.p, color.names.p[1:19])
colnames(labels) <- c("Species", "Shape", "Color")

label.names.p1 <- c("Phytophthora sansomeana",
                    "Pythium aff. dissotocum",
                    "Pythium lutarium",
                    "Pythium oopapillum",
                    "Pythium irregulare",
                    "Pythium spinosum",
                    "Pythium sylvaticum",
                    "Pythium glomeratum",
                    "Pythium ultimum var. ultimum",
                    "Pythium perplexum",
                    "Phytophthora sojae",
                    "Pythium pleroticum",
                    "Pythium ultimum var. sporangiiferum",
                    "Phytopythium litorale",
                    "Pythium intermedium")
shapes.p1 <- labels$Shape[labels$Species %in% label.names.p1]
color.names.p1 <- labels$Color[labels$Species %in% label.names.p1]
labels$EC50.plot <- labels$Species %in% levels(EC50$species_od)
```
```{r}
 p <- ggplot(cor.plot.relgrowth, aes(y = odrelgrowth, x = ppmeanrelgrowth)) +
    geom_point(aes(shape = species, color = species), size = 4) +
    scale_y_continuous(limits = c(0, 125), breaks = c(0, 25, 50, 75, 100, 125)) +
    scale_x_continuous(limits = c(0, 125), breaks = c(0, 25, 50, 75, 100, 125)) +
     geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x, fullrange = TRUE) +
  stat_poly_eq(formula = y ~ x, 
               aes(label = paste(..eq.label.., ..adj.rr.label.., sep = "~~~")), 
               parse = TRUE, size = 5) +
    xlab("% Relative Growth, Poison Plate") + 
    ylab("% Relative Growth, Optical Density") + 
    theme_classic() +
    scale_shape_manual(name = "Species", 
                      labels = as.character(labels$Species[labels$Species %in% levels(cor.plot.relgrowth$species)]),
                      values = labels$Shape[labels$Species %in% levels(cor.plot.relgrowth$species)]) +
    scale_colour_manual(name = "Species",
                      labels = as.character(labels$Species[labels$Species %in% levels(cor.plot.relgrowth$species)]),
                      values = as.character(labels$Color[labels$Species %in% levels(cor.plot.relgrowth$species)])) +   
    theme(axis.text.x = element_text(size = 15, face = "bold", family = "serif"),
          axis.text.y = element_text(size = 15, face = "bold", family = "serif"),
          axis.title.x = element_text(size = 15, face = "bold", family = "serif"),
          axis.title.y = element_text(size = 15, face = "bold", family = "serif"),
          axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
          axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
          legend.text = element_text(size = 10, face = "bold.italic", family = "serif"),
          legend.key = element_blank(),
          legend.title = element_text(size = 10, face="bold", family = "serif"),
          legend.position = "bottom", 
          strip.text.x = element_text(size = 15, face = "bold", family = "serif")) + 
   facet_wrap(~chem)


EC50 <- EC50[order(as.character(EC50$species_pp)),]
x <- levels(EC50$species_pp)
x <- x[order(levels(EC50$species_pp))]

p1 <- ggplot(EC50, aes(mean.abs.pp, mean.abs.od)) + 
  geom_point(aes(color = factor(species_pp,levels = x), shape = factor(species_pp,levels = x)), size = 4) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x, fullrange = TRUE) +
  stat_poly_eq(formula = y ~ x, 
               aes(label = paste(..eq.label.., ..adj.rr.label.., sep = "~~~")), 
               parse = TRUE, size = 5) +
  scale_shape_manual(name = "Species", 
                      labels = as.character(labels$Species[labels$Species %in% levels(EC50$species_pp)]),
                      values = labels$Shape[labels$Species %in% levels(EC50$species_pp)]) +
    scale_colour_manual(name = "Species",
                      labels = as.character(labels$Species[labels$Species %in% levels(EC50$species_pp)]),
                      values = as.character(labels$Color[labels$Species %in% levels(EC50$species_pp)])) + 
  xlab(expression(bold("Poison plate EC"[50]))) + 
  ylab(expression(bold("Optical density EC"[50]))) + 
  theme_classic() + 
  theme(axis.text.x = element_text(size = 15, face = "bold", family = "serif"),
        axis.text.y = element_text(size = 15, face = "bold", family = "serif"),
        axis.title.x = element_text(size = 15, face = "bold", family = "serif"),
        axis.title.y = element_text(size = 15, face = "bold", family = "serif"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.text = element_text(size = 10, face = "bold.italic", family = "serif"),
        legend.key = element_blank(),
        legend.title = element_text(size = 10, face="bold", family = "serif"),
        strip.text.x = element_text(size = 15, face = "bold", family = "serif")) +
  facet_wrap(~chem2)
```
```{r}
#extract legend
#https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(p)
```
```{r, fig.width=6}
p3 <- grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p + theme(legend.position="none"),
                         nrow=2),
             mylegend, nrow=2,heights=c(7, 1))
print(p3)
#ggsave(file="FigureCorrelation.pdf", plot = p3, width = 12, height = 9, dpi = 300)
```







