---
title: "Z-Factor"
author: "Zachary Noel"
date: "1/26/2017"
output:
  md_document:
    variant: markdown_github
---

Start: 

I include this header at the top of all code I write. 

```{r eval=FALSE, include=FALSE}
rm(list = ls(all=TRUE)) # removes all variables in the global environment so you start fresh

Sys.time() # prints out the time and date you ran the code

options(scipen = 999) # stops anything from being in scientific notation

op <- par(oma=c(5,7,1,1))
```

```{r}
# ipak function: install and load multiple R packages.
# check to see if packages are installed. Install them if they are not, then load them into the R session.
# Source: https://gist.github.com/stevenworthington/3178163
ipak <- function(pkg){
new.pkg <- pkg[!(pkg %in% installed.packages()[,"Package"])]
if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
sapply(pkg, require, character.only = TRUE)
}
```

###Libraries
```{r Libraries, include=TRUE, message=FALSE, warning=FALSE}
packages <- c("drc", "lme4", "lsmeans", "plyr", "plotrix", "knitr", "ggplot2", "lmtest", "lmerTest", "Rmisc", "gridExtra", "plotly", "webshot", "ggpmisc", "ggsci","scales")
ipak(packages)
```

###Read Data
```{r}
ass.qual <- data.frame(read.csv("ass_quality_AllData.csv", na.strings = "na"))
```

###Z'factor analysis

We are going to use the ass.qual dataset first to follow the assay quality experiment proposed by chai et al 2015. 

First lets just look at the dynamic ranges and the standard deviations that we will use to calculate Z factor
```{r}
mef.qual <- ass.qual[ass.qual$fungicide == "mefenoxam",]
mef.qual$fungicide <- factor(mef.qual$fungicide)
eth.qual <- ass.qual[ass.qual$fungicide == "ethaboxam",]
eth.qual$fungicide <- factor(eth.qual$fungicide)

ggplot(eth.qual, aes(column, row)) + 
  geom_tile(aes(fill = od600)) + 
  scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() +
  facet_wrap(~daynum*platenum)

ggplot(mef.qual, aes(column, row)) + 
  geom_tile(aes(fill = od600)) + 
  scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() +
  facet_wrap(~daynum*platenum)

levels(ass.qual$fungicide) <- c("Ethaboxam", "Mefenoxam")

qplot(od600, data=ass.qual, geom="density", fill=trt, alpha=I(.5),
   main="", xlab="Optical Density",
   ylab="Density") + 
  facet_wrap(~fungicide) + 
  theme_classic() +
  scale_fill_npg() +
  guides(fill = guide_legend(title = "Treatment", title.position = "top")) +
  theme(axis.text.x = element_text(size = 15, face = "bold", family = "serif"),
          axis.text.y = element_text(size = 15, face = "bold", family = "serif"),
          axis.title.x = element_text(size = 15, face = "bold", family = "serif"),
          axis.title.y = element_text(size = 15, face = "bold", family = "serif"),
          axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
          axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
          legend.text = element_text(size = 10, face = "bold", family = "serif"),
          legend.key = element_blank(),
          legend.title = element_text(size = 10, face="bold", family = "serif"),
          legend.position = "right", 
          strip.text.x = element_text(size = 15, face = "bold", family = "serif"),
        title = element_text(size = 16, family = "serif"))

ass_qual_well <- NULL
ass_qual_plate <- NULL
for (day in 1:3){
  for (plate in 1:3){

    #well to well
    mean.mef.0 <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "0ppm"])
    sd.mef.0 <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "0ppm"])
    mean.mef.10 <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "10ppm"])
    sd.mef.10 <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "10ppm"])
    mean.mef.blank <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "blank"])
    sd.mef.blank <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "blank"])
    
   mean.eth.0 <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "0ppm"])
    sd.eth.0 <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "0ppm"])
    mean.eth.20 <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "20ppm"])
    sd.eth.20 <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "20ppm"])
   mean.eth.blank <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "blank"])
    sd.eth.blank <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$plate == plate & ass.qual$trt == "blank"])
    
    ass_qual_i <- cbind(day, plate, mean.mef.0, sd.mef.0, mean.mef.10, sd.mef.10, mean.mef.blank, sd.mef.blank,
                        mean.eth.0, sd.eth.0, mean.eth.20, sd.eth.20, mean.eth.blank, sd.eth.blank) 
    ass_qual_well <- rbind(ass_qual_well, ass_qual_i)
    
    
    
   
  }
  #plate to plate
    mean.mef.0.plate <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$trt == "0ppm"])
    sd.mef.0.plate <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$trt == "0ppm"])
    mean.mef.10.plate <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$trt == "10ppm"])
    sd.mef.10.plate <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$trt == "10ppm"])
    mean.mef.blank.plate <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$trt == "blank"])
    sd.mef.blank.plate <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$day == day & ass.qual$trt == "blank"])
    
    mean.eth.0.plate <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$trt == "0ppm"])
    sd.eth.0.plate <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$trt == "0ppm"])
    mean.eth.20.plate <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$trt == "20ppm"])
    sd.eth.20.plate <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$trt == "20ppm"])
    mean.eth.blank.plate <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$trt == "blank"])
    sd.eth.blank.plate <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$day == day & ass.qual$trt == "blank"])
    
    ass_qual_j <- cbind(day, mean.mef.0.plate, sd.mef.0.plate, mean.mef.10.plate, sd.mef.10.plate, mean.mef.blank.plate,
                            sd.mef.blank.plate,mean.eth.0.plate, sd.eth.0.plate, mean.eth.20.plate, sd.eth.20.plate, 
                            mean.eth.blank.plate, sd.eth.blank.plate) 
    ass_qual_plate <- rbind(ass_qual_plate, ass_qual_j)
    
}
 #day to day 
    mean.mef.0.day <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$trt == "0ppm"])
    sd.mef.0.day <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$trt == "0ppm"])
    mean.mef.10.day <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$trt == "10ppm"])
    sd.mef.10.day <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$trt == "10ppm"])
    mean.mef.blank.day <- mean(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$trt == "blank"])
    sd.mef.blank.day <- sd(ass.qual$od600[ass.qual$fungicide == "mefenoxam" & ass.qual$trt == "blank"])
    
    mean.eth.0.day <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$trt == "0ppm"])
    sd.eth.0.day <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$trt == "0ppm"])
    mean.eth.20.day <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$trt == "20ppm"])
    sd.eth.20.day <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$trt == "20ppm"])
    mean.eth.blank.day <- mean(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$trt == "blank"])
    sd.eth.blank.day <- sd(ass.qual$od600[ass.qual$fungicide == "ethaboxam" & ass.qual$trt == "blank"])
    
    ass_qual_y <- cbind(mean.mef.0.day, sd.mef.0.day, mean.mef.10.day, sd.mef.10.day, mean.mef.blank.day,
                            sd.mef.blank.day,mean.eth.0.day, sd.eth.0.day, mean.eth.20.day, sd.eth.20.day, 
                            mean.eth.blank.day, sd.eth.blank.day) 
    
#write.csv(ass_qual_y, "ass_qual_day.csv")
#write.csv(ass_qual_plate, "ass_qual_plate.csv")
#write.csv(ass_qual_well, "ass_qual_well.csv")

```

mefenoxam z' scores
```{r}
Z <- function (sdPC, sdNC, mPC, mNC) {1-((3*(sdPC + sdNC))/abs(mPC - mNC))}
qc.ethaboxam <- ass.qual[ass.qual$fungicide == "Ethaboxam",]
qc.ethaboxam_day1 <- qc.ethaboxam[qc.ethaboxam$day == 1,]
qc.ethaboxam_day2 <- qc.ethaboxam[qc.ethaboxam$day == 2,]
qc.ethaboxam_day3 <- qc.ethaboxam[qc.ethaboxam$day == 3,]
qc.mefenoxam <- ass.qual[ass.qual$fungicide == "Mefenoxam",]
qc.mefenoxam_day1 <- qc.mefenoxam[qc.mefenoxam$day == 1,]
qc.mefenoxam_day2 <- qc.mefenoxam[qc.mefenoxam$day == 2,]
qc.mefenoxam_day3 <- qc.mefenoxam[qc.mefenoxam$day == 3,]


#Mefenoxam Z' factor scores day 1

#well-to-well plate 1
qc.mefenoxam_plate1 <- qc.mefenoxam_day1[qc.mefenoxam_day1$plate == 1,]
meanPC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate1_well_day1 <- data.frame("mefenoxam_plate1_well_day1", PC_NC, PC_NTC, NC_NTC);
names(Z_prime_plate1_well_day1) <- letters[1:4]

#well-to-well plate 2
qc.mefenoxam_plate2 <- qc.mefenoxam_day1[qc.mefenoxam_day1$plate == 2,]
meanPC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate2_well_day1 <- data.frame("mefenoxam_plate2_well_day1", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate2_well_day1) <- letters[1:4]

#well-to-well plate 3
qc.mefenoxam_plate3 <- qc.mefenoxam_day1[qc.mefenoxam_day1$plate == 3,]
meanPC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate3_well_day1 <- data.frame("mefenoxam_plate3_well_day1", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate3_well_day1) <- letters[1:4]

#plate-to-plate day 1
meanPC <- mean(qc.mefenoxam_day1$od600[qc.mefenoxam_day1$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_day1$od600[qc.mefenoxam_day1$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_day1$od600[qc.mefenoxam_day1$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_day1$od600[qc.mefenoxam_day1$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_day1$od600[qc.mefenoxam_day1$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_day1$od600[qc.mefenoxam_day1$trt == "blank"])
  
PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate_day1 <- data.frame("mefenoxam_plate_day1", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate_day1) <- letters[1:4]

#Mefenoxam Z' factor scores day 2

#well-to-well plate 1
qc.mefenoxam_plate1 <- qc.mefenoxam_day2[qc.mefenoxam_day2$plate == 1,]
meanPC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate1_well_day2 <- data.frame("mefenoxam_plate1_well_day2", PC_NC, PC_NTC, NC_NTC);
names(Z_prime_plate1_well_day2) <- letters[1:4]

#well-to-well plate 2
qc.mefenoxam_plate2 <- qc.mefenoxam_day2[qc.mefenoxam_day2$plate == 2,]
meanPC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate2_well_day2 <- data.frame("mefenoxam_plate2_well_day2", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate2_well_day2) <- letters[1:4]

#well-to-well plate 3
qc.mefenoxam_plate3 <- qc.mefenoxam_day2[qc.mefenoxam_day2$plate == 3,]
meanPC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate3_well_day2 <- data.frame("mefenoxam_plate3_well_day2", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate3_well_day2) <- letters[1:4]

#plate-to-plate day 2
meanPC <- mean(qc.mefenoxam_day2$od600[qc.mefenoxam_day2$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_day2$od600[qc.mefenoxam_day2$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_day2$od600[qc.mefenoxam_day2$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_day2$od600[qc.mefenoxam_day2$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_day2$od600[qc.mefenoxam_day2$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_day2$od600[qc.mefenoxam_day2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate_day2 <- data.frame("mefenoxam_plate_day2", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate_day2) <- letters[1:4]

#Mefenoxam Z' factor scores day 3

#well-to-well plate 1
qc.mefenoxam_plate1 <- qc.mefenoxam_day3[qc.mefenoxam_day3$plate == 1,]
meanPC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate1$od600[qc.mefenoxam_plate1$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate1_well_day3 <- data.frame("mefenoxam_plate1_well_day3", PC_NC, PC_NTC, NC_NTC);
names(Z_prime_plate1_well_day3) <- letters[1:4]

#well-to-well plate 2
qc.mefenoxam_plate2 <- qc.mefenoxam_day3[qc.mefenoxam_day3$plate == 2,]
meanPC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate2$od600[qc.mefenoxam_plate2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate2_well_day3 <- data.frame("mefenoxam_plate2_well_day3", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate2_well_day3) <- letters[1:4]

#well-to-well plate 3
qc.mefenoxam_plate3 <- qc.mefenoxam_day3[qc.mefenoxam_day3$plate == 3,]
meanPC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_plate3$od600[qc.mefenoxam_plate3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate3_well_day3 <- data.frame("mefenoxam_plate3_well_day3", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate3_well_day3) <- letters[1:4]

#plate-to-plate day 2
meanPC <- mean(qc.mefenoxam_day3$od600[qc.mefenoxam_day3$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam_day3$od600[qc.mefenoxam_day3$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam_day3$od600[qc.mefenoxam_day3$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam_day3$od600[qc.mefenoxam_day3$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam_day3$od600[qc.mefenoxam_day3$trt == "blank"])
sdNTC <- sd(qc.mefenoxam_day3$od600[qc.mefenoxam_day3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate_day3 <- data.frame("mefenoxam_plate_day3", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate_day3) <- letters[1:4]

#day-to-day 
meanPC <- mean(qc.mefenoxam$od600[qc.mefenoxam$trt == "10ppm"])
sdPC <- sd(qc.mefenoxam$od600[qc.mefenoxam$trt == "10ppm"])
meanNC <- mean(qc.mefenoxam$od600[qc.mefenoxam$trt == "0ppm"])
sdNC <- sd(qc.mefenoxam$od600[qc.mefenoxam$trt == "0ppm"])
meanNTC <- mean(qc.mefenoxam$od600[qc.mefenoxam$trt == "blank"])
sdNTC <- sd(qc.mefenoxam$od600[qc.mefenoxam$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_day <- data.frame("mefenoxam_day", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_day) <- letters[1:4]

#all Z'factors in one table

Zfactor_mef <- rbind.data.frame(Z_prime_plate1_well_day1, 
                                Z_prime_plate2_well_day1, 
                                Z_prime_plate3_well_day1,
                                Z_prime_plate1_well_day2, 
                                Z_prime_plate2_well_day2, 
                                Z_prime_plate3_well_day2,
                                Z_prime_plate1_well_day3, 
                                Z_prime_plate2_well_day3, 
                                Z_prime_plate3_well_day3,
                                Z_prime_plate_day1,
                                Z_prime_plate_day2,
                                Z_prime_plate_day3,
                                Z_prime_day)

names(Zfactor_mef) <- c("Comparison", 
                        "10-0",
                        "10-blank",
                        "0-blank")
#write.csv(Zfactor_mef, "Zfactor_mefenoxam.csv") 

```

Plot of mefenoxam dynamic range
```{r, warning=FALSE}
library(ggplot2)
p <- ggplot(qc.mefenoxam, aes(well, od600))
p + geom_point(aes(colour = factor(trt)), size = 4) +
  theme_bw() +
  scale_x_continuous(breaks = seq(from = 1, to = 96, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.2)) +
  labs(list(x = "Wells of microtiter plate",  
            y = expression(bold("OD"[600])))) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 30, face = "bold"),
        axis.title.y = element_text(size = 30, face = "bold"),
        legend.text = element_text(size  = 20, face = "bold"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        strip.text = element_text(size=15, face = "bold"),
        panel.margin=unit(0 , "lines"),
        axis.ticks = element_blank()) +
  facet_wrap(~ daynum*platenum, nrow = 1)
```

Plot of mefenoxam dynamic range broken up by day to day
```{r, warning=FALSE}
p <- ggplot(qc.mefenoxam, aes(well, od600))
p + geom_point(aes(colour = factor(trt)), size = 4) +
  theme_bw() +
  scale_x_continuous(breaks = seq(from = 1, to = 96, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.2)) +
  labs(list(x = "Wells of microtiter plate",  
            y = expression(bold("OD"[600])))) +
  theme(axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 30, face = "bold"),
        axis.title.y = element_text(size = 30, face = "bold"),
        legend.text = element_text(size  = 20, face = "bold"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        strip.text = element_text(size=18, face = "bold"))
```

ethaboxam z scores
```{r}
#ethaboxam Z' factor scores day 1

#well-to-well plate 1
qc.ethaboxam_plate1 <- qc.ethaboxam_day1[qc.ethaboxam_day1$plate == 1,]
meanPC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate1_well_day1 <- data.frame("ethaboxam_plate1_well_day1", PC_NC, PC_NTC, NC_NTC);
names(Z_prime_plate1_well_day1) <- letters[1:4]

#well-to-well plate 2
qc.ethaboxam_plate2 <- qc.ethaboxam_day1[qc.ethaboxam_day1$plate == 2,]
meanPC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate2_well_day1 <- data.frame("ethaboxam_plate2_well_day1", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate2_well_day1) <- letters[1:4]

#well-to-well plate 3
qc.ethaboxam_plate3 <- qc.ethaboxam_day1[qc.ethaboxam_day1$plate == 3,]
meanPC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate3_well_day1 <- data.frame("ethaboxam_plate3_well_day1", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate3_well_day1) <- letters[1:4]

#plate-to-plate day 1
meanPC <- mean(qc.ethaboxam_day1$od600[qc.ethaboxam_day1$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_day1$od600[qc.ethaboxam_day1$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_day1$od600[qc.ethaboxam_day1$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_day1$od600[qc.ethaboxam_day1$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_day1$od600[qc.ethaboxam_day1$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_day1$od600[qc.ethaboxam_day1$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate_day1 <- data.frame("ethaboxam_plate_day1", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate_day1) <- letters[1:4]

#ethaboxam Z' factor scores day 2

#well-to-well plate 1
qc.ethaboxam_plate1 <- qc.ethaboxam_day2[qc.ethaboxam_day2$plate == 1,]
meanPC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate1_well_day2 <- data.frame("ethaboxam_plate1_well_day2", PC_NC, PC_NTC, NC_NTC);
names(Z_prime_plate1_well_day2) <- letters[1:4]

#well-to-well plate 2
qc.ethaboxam_plate2 <- qc.ethaboxam_day2[qc.ethaboxam_day2$plate == 2,]
meanPC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate2_well_day2 <- data.frame("ethaboxam_plate2_well_day2", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate2_well_day2) <- letters[1:4]

#well-to-well plate 3
qc.ethaboxam_plate3 <- qc.ethaboxam_day2[qc.ethaboxam_day2$plate == 3,]
meanPC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate3_well_day2 <- data.frame("ethaboxam_plate3_well_day2", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate3_well_day2) <- letters[1:4]

#plate-to-plate day 2
meanPC <- mean(qc.ethaboxam_day2$od600[qc.ethaboxam_day2$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_day2$od600[qc.ethaboxam_day2$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_day2$od600[qc.ethaboxam_day2$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_day2$od600[qc.ethaboxam_day2$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_day2$od600[qc.ethaboxam_day2$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_day2$od600[qc.ethaboxam_day2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate_day2 <- data.frame("ethaboxam_plate_day2", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate_day2) <- letters[1:4]

#ethaboxam Z' factor scores day 3

#well-to-well plate 1
qc.ethaboxam_plate1 <- qc.ethaboxam_day3[qc.ethaboxam_day3$plate == 1,]
meanPC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate1$od600[qc.ethaboxam_plate1$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate1_well_day3 <- data.frame("ethaboxam_plate1_well_day3", PC_NC, PC_NTC, NC_NTC);
names(Z_prime_plate1_well_day3) <- letters[1:4]

#well-to-well plate 2
qc.ethaboxam_plate2 <- qc.ethaboxam_day3[qc.ethaboxam_day3$plate == 2,]
meanPC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate2$od600[qc.ethaboxam_plate2$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate2_well_day3 <- data.frame("ethaboxam_plate2_well_day3", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate2_well_day3) <- letters[1:4]

#well-to-well plate 3
qc.ethaboxam_plate3 <- qc.ethaboxam_day3[qc.ethaboxam_day3$plate == 3,]
meanPC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_plate3$od600[qc.ethaboxam_plate3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate3_well_day3 <- data.frame("ethaboxam_plate3_well_day3", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate3_well_day3) <- letters[1:4]

#plate-to-plate day 2
meanPC <- mean(qc.ethaboxam_day3$od600[qc.ethaboxam_day3$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam_day3$od600[qc.ethaboxam_day3$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam_day3$od600[qc.ethaboxam_day3$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam_day3$od600[qc.ethaboxam_day3$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam_day3$od600[qc.ethaboxam_day3$trt == "blank"])
sdNTC <- sd(qc.ethaboxam_day3$od600[qc.ethaboxam_day3$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_plate_day3 <- data.frame("ethaboxam_plate_day3", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_plate_day3) <- letters[1:4]

#day-to-day 
meanPC <- mean(qc.ethaboxam$od600[qc.ethaboxam$trt == "20ppm"])
sdPC <- sd(qc.ethaboxam$od600[qc.ethaboxam$trt == "20ppm"])
meanNC <- mean(qc.ethaboxam$od600[qc.ethaboxam$trt == "0ppm"])
sdNC <- sd(qc.ethaboxam$od600[qc.ethaboxam$trt == "0ppm"])
meanNTC <- mean(qc.ethaboxam$od600[qc.ethaboxam$trt == "blank"])
sdNTC <- sd(qc.ethaboxam$od600[qc.ethaboxam$trt == "blank"])

PC_NC <- Z(sdPC, sdNC, meanPC, meanNC) #inhibited growth compared to non-inhibited growth
PC_NTC <- Z(sdPC, sdNTC, meanPC, meanNTC) #inhibited growth compared to blank control wells
NC_NTC <- Z(sdNC, sdNTC, meanNC, meanNTC) #non-inhibited growth compared to blank control wells

Z_prime_day <- data.frame("ethaboxam_day", PC_NC, PC_NTC, NC_NTC)
names(Z_prime_day) <- letters[1:4]

#all Z'factors in one table


Zfactor_eth <- rbind.data.frame(Z_prime_plate1_well_day1, 
                                Z_prime_plate2_well_day1, 
                                Z_prime_plate3_well_day1,
                                Z_prime_plate1_well_day2, 
                                Z_prime_plate2_well_day2, 
                                Z_prime_plate3_well_day2,
                                Z_prime_plate1_well_day3, 
                                Z_prime_plate2_well_day3, 
                                Z_prime_plate3_well_day3,
                                Z_prime_plate_day1,
                                Z_prime_plate_day2,
                                Z_prime_plate_day3,
                                Z_prime_day)
#write.csv(Zfactor_eth, "Zfactor_ethaboxam.csv") 

names(Zfactor_eth) <- c("Comparison", 
                        "10-0",
                        "10-blank",
                        "0-blank")

```

Plot of ethaboxam dynamic range
```{r, warning=FALSE}
p <- ggplot(qc.ethaboxam, aes(well, od600))
p + geom_point(aes(colour = factor(trt)), size = 4) +
  theme_bw() +
  scale_x_continuous(breaks = seq(from = 1, to = 96, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.2)) +
  labs(list(x = "Wells of microtiter plate",  
            y = expression(bold("OD"[600])))) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 30, face = "bold"),
        axis.title.y = element_text(size = 30, face = "bold"),
        legend.text = element_text(size  = 20, face = "bold"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        strip.text = element_text(size=15, face = "bold"),
        panel.margin=unit(0 , "lines"),
        axis.ticks = element_blank()) +
  facet_wrap(~ daynum*platenum, nrow = 1)
```

plot of ethaboxam dynamic range broken up by day to day
```{r, warning=FALSE}
p <- ggplot(qc.ethaboxam, aes(well, od600))
p + geom_point(aes(colour = factor(trt)), size = 4) +
  theme_bw() +
  scale_x_continuous(breaks = seq(from = 1, to = 96, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.2)) +
  labs(list(x = "Wells of microtiter plate",  
            y = expression(bold("OD"[600])))) +
  theme(axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 18, face = "bold"),
        axis.title.x = element_text(size = 30, face = "bold"),
        axis.title.y = element_text(size = 30, face = "bold"),
        legend.text = element_text(size  = 20, face = "bold"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        strip.text = element_text(size=20, face = "bold"))
```